A Large-Scale Study of the Use of Eval in R

### 2020-11-05 inst/paper/main.tex
Change heading
Add key points to discuss for how dangerous is eval

\section{Analysis of Eval}

@@

>>>>

\section{Evaluation}

@@

\subsubsection{How much code is executed inside eval}
- measure number of operations inside eval and outside eval.
- this is useful because if analyzers treat eval as a nop, they may miss X\% of the code.

\subsubsection{Does eval create observable side-effects}
- measure number of reads and writes by eval outside of its ``bubble''.
- Since R is lazy, even reads can cause promise evaluation and hence, side-effects.
- Look at writes to non-local scopes. Compare with total number of writes for
reference?
- Categorize side-effects between env passed to eval and other envs.

\subsubsection{Does eval do reflection}
\eval can access parent scopes via reflection. Find number of times it does that
and the depth to which it access parent frames.

\subsubsection{Does eval introduce new bindings}
Find number of times, eval introduces new bindings. There are many ways -- library,
load, attach, source, and explicitly introduce bindings using super-assign, assign and define.

\subsubsection{Does eval call C code}
Find number of times, eval makes call to native code using - .Call, .External,
etc. Find out if there are native functions that are called only from within eval.

\subsubsection{Does eval add finalizers}
Eval can attach code to be executed when the object goes out of scope or program
exits. Find if eval does that.

\subsubsection{Does eval do non-local returns}
Eval can do non-local returns effective bypassing evaluation of the rest of the
function. This can be useful for static analyzers.

Conclude with number of evals that are ``pure'', i.e. evals which
could be ignored by a static analyzer without any problem.
